---
title: "rCharts"

output: slidy_presentation
---



## install & test

#install.packages("devtools")
#require(devtools)
#install_github('rCharts', 'ramnathv')

```{r}
require(rCharts)
head(iris)

names(iris)
names(iris) = gsub("\\.", "", names(iris))
names(iris)
```

```{r}
require(rCharts)
<<<<<<< HEAD
=======
<<<<<<< HEAD
>>>>>>> 45f58493d955ffa5342d4391b32315bdfcf0c378
require(knitr)
opts_chunk$set(comment = NA, results = "test", comment = NA, tidy = F)
r1 <- rPlot(SepalLength ~ SepalWidth | Species, data = iris, color = 'Species', type = 'point')
r1$save('test.html', cdn = TRUE)
r1$show('iframesrc', cdn = TRUE)
<<<<<<< HEAD
=======
=======
r1 <- rPlot(SepalLength ~ SepalWidth | Species, data = iris, color = 'Species', type = 'point')
r1$save('test.html', cdn = TRUE)

>>>>>>> a5e06a1157f5aec0e1a68a312265c59cd0326cb6
>>>>>>> 45f58493d955ffa5342d4391b32315bdfcf0c378
# <iframe width = "800" height = "600" src='r1.html'></iframe>
```


<iframe width = 100% height = 60% src='test.html'></iframe>



## Polycharts

```{r}
head(mtcars)

r2 <- rPlot(mpg ~ wt, data = mtcars, type = 'point')
r2$save('r2.html', cdn = TRUE)

```

<iframe width = 100% height = 60% src='r2.html'></iframe>


### rCharts Polychart: Adding horizontal or vertical lines to a plot


<http://stackoverflow.com/questions/20107947/rcharts-polychart-adding-horizontal-or-vertical-lines-to-a-plot>


```{r}
mtcars$avg <- mean(mtcars$mpg)
mtcars$sdplus <- mtcars$avg + sd(mtcars$mpg)
mtcars$sdneg <-  mtcars$avg - sd(mtcars$mpg)
p1 <- rPlot(mpg~wt, data=mtcars, type='point')

p1$layer(y='avg', copy_layer=T, type='line', color=list(const='red'))
p1$layer(y='sdplus', copy_layer=T, type='line', color=list(const='green'))
p1$layer(y='sdneg', copy_layer=T, type='line', color=list(const='green'))

p1$save('p1.html', cdn = TRUE)

```

<iframe width = 100% height = 60% src='p1.html'></iframe>

### 다양한 polycharts

<https://rpubs.com/kohske/12331>

- point

```{r}
p2 <- rPlot( mpg ~ qsec, data = mtcars, color = "cyl", size = "disp", type = "point")

p2$layer(tooltip = "#! function(i) {return 'gear ' + i.gear + ' level';} !#", copy_layer = TRUE)

# p$show("inline", include_assets = FALSE) 

p2$save('p2.html', cdn = TRUE)

```

<iframe width = 100% height = 60% src='p2.html'></iframe>


- line + point

```{r}
d <- expand.grid(x = 1:10, g = letters[1:3])
d$y <- rnorm(nrow(d))
p3 <- rPlot( y ~ x, data = d, color = "g", type = "line")
p3$layer(y ~ x, data = d, color = "g", type = "point")
p3$set(title = "line + point")
# p3$show("inline", include_assets = FALSE)
p3$save('p3.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='p3.html'></iframe>

- area

```{r}
d <- expand.grid(x = 1:10, g = letters[1:3])
d$y <- runif(nrow(d))
p4 <- rPlot( y ~ x, data = d, color = "g", type = "area")
# p4$guides("#! {y: {title: 'hoge', scale: {type: 'log'}}}")
p4$guides(x = list(title = "XXXX"), y = list(title = "YYYY"))
# p4$show("inline", include_assets = FALSE)
p4$save('p4.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='p4.html'></iframe>


- bar

```{r}
hair_eye <- as.data.frame(HairEyeColor)

p5 <- rPlot(Freq ~ Hair | Sex, color = "Eye", data = hair_eye, type = "bar", position = "dodge")

p5$save('p5.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='p5.html'></iframe>


- 극좌표


```{r}
d <- expand.grid(x = 1:10, g = letters[1:3])
d$y <- runif(nrow(d))

p6 <- rPlot(y ~ x | g, color = "x", data = d, type = "bar")

p6$params$layers[[1]]$x <- NULL # x 삭제
p6$coord(type = "polar") # 파이차트

p6$guides(x = list(position = "none", padding = 0), y = list(numticks=10)) # 축 변경

p6$save('p6.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='p6.html'></iframe>



## Morris

```{r}
data(economics, package = "ggplot2")
econ <- transform(economics, date = as.character(date))
m1 <- mPlot(x = "date", y = c("psavert", "uempmed"), type = "Line", data = econ)
m1$set(pointSize = 0, lineWidth = 1)
m1$save('m1.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='m1.html'></iframe>

### 다양한 polycharts

<https://rpubs.com/kohske/12406>

- line 1

```{r}
# plot 생성
m2 <- mPlot(y ~ x, data = data.frame(x = paste(2001:2005), y = rnorm(1:5)), type = "Line", smooth = FALSE)
# grid & axes 설정
m2$set(grid = FALSE, axes = FALSE)
# line color
m2$set(lineColors = list("skyblue"))
# p$show("inline", include_assets = FALSE)
m2$save('m2.html', cdn = TRUE)
## Loading required package: reshape2
```

<iframe width = 100% height = 60% src='m2.html'></iframe>

- line 2

```{r}
d <- data.frame(x = paste(2001:2010), y1 = runif(10), y2 = runif(10))
m3 <- mPlot(x = "x", y = c("y1", "y2"), data = d, type = "Line", labels = c("line 1", "line 2"))
m3$save('m3.html', cdn = TRUE)

```

<iframe width = 100% height = 60% src='m3.html'></iframe>

- 시계열 영역 차트

```{r}
d <- data.frame(x = paste(2001:2010), y1 = runif(10), y2 = runif(10), y3 = runif(10))

m4 <- mPlot(x = "x", y = c("y1", "y2", "y3"), data = d, type = "Area", smooth=FALSE, pointSize = 10, lineWidth = 5)

# event 옵션추가
m4$set(events = paste(c(2004, 2008)), eventStrokeWidth = 10)
m4$save('m4.html', cdn = TRUE)

```

<iframe width = 100% height = 60% src='m4.html'></iframe>

- 사용자정의 popup tooltip

```{r}
d <- data.frame(x = paste(2001:2010), y1 = runif(10), y2 = runif(10), ch = letters[1:10])
m5 <- mPlot(x = "x", y = c("y1", "y2"), data = d, type = "Line", labels = c("line 1", "line 2"))
# tooltip 에 대한 콜백함수 설정
m5$set(hoverCallback = "#! function (index, options, content) {return options.data[index].ch;} !#")
m5$save('m5.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='m5.html'></iframe>



- bar 1

```{r}
d <- data.frame(x = paste(2001:2010), y1 = runif(10), y2 = runif(10), y3 = runif(10))
m6 <- mPlot(x = "x", y = c("y1", "y2", "y3"), data = d, type = "Bar", barColors = c("red", "green", "blue"))
m6$save('m6.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='m6.html'></iframe>


- bar 2 ; stacked

```{r}
d <- data.frame(x = paste(2001:2010), y1 = runif(10), y2 = runif(10), y3 = runif(10))

m7 <- mPlot(x = "x", y = c("y1", "y2", "y3"), data = d, type = "Bar", stacked = TRUE, barColors = c("red", "green", "blue"))

m7$save('m7.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='m7.html'></iframe>


- 도넛차트

```{r}
d <- data.frame(label = c("'92 live", "'95 secret", "'98 age", "'02 garden"), value = c(32, 30, 25, 38))
m8 <- mPlot(x = NULL, y = NULL, data = d, type = "Donut", formatter = "#! function (y) { return('rate'+y+'%!!'); } !#")

m8$save('m8.html', cdn = TRUE)
```

<iframe width = 100% height = 60% src='m8.html'></iframe>




## nvd3

### Why?????????????

```{r}
hair_eye = as.data.frame(HairEyeColor)
r3 <- nPlot(Freq ~ Hair, group = 'Eye',data = subset(hair_eye, Sex =="Female",type = 'multiBarChart'))
r3$chart(color = c('brown', 'blue', '#594c26', 'green'))
r3$save('r3.html', cdn = TRUE)

```

<iframe width = 100% height = 60%  src='r3.html'></iframe>



## xCharts

```{r}
library(reshape2)
uspexp <- melt(USPersonalExpenditure)
names(uspexp)[1:2] = c("category", "year")
x1 <- xPlot(value ~ year, group = "category", data = uspexp, type = "line-dotted")
x1$save('x1.html', cdn = TRUE)

```

<iframe width = 100% height = 60%  src='x1.html'></iframe>



## Rickshaw

```{r}
head(USPersonalExpenditure)
usp = reshape2::melt(USPersonalExpenditure)
head(usp)
tail(usp)

tt <- as.POSIXct(paste0(usp$Var2, "-01-01"))
tt
usp$Var2 <- as.numeric(as.POSIXct(paste0(usp$Var2, "-01-01")))
usp$Var2 
pp4 <- Rickshaw$new()

pp4$layer(value ~ Var2, group = "Var1", data = usp, type = "area")
pp4$set(slider = TRUE)

pp4$save('pp4.html', cdn = TRUE)

```

<iframe width = 100% height = 60%  src='pp4.html'></iframe>



## Leaflet

<http://leafletjs.com/>



```{r}
map3 <- Leaflet$new()
map3$setView(c(37.5414623,127.0722618), zoom = 17)
map3$marker(c(37.5414623,127.0722618), bindPopup = "<p> Hi. I'm Here! </p>")

map3$save('map3.html', cdn = TRUE)

```

<iframe width = 100% height = 60%  src='map3.html'></iframe>




## Interactive Controls and rCharts 1

참고 : <http://rcharts.io/icontrols/#.VE4CJCKsV8E>

```{r}
n1 <- rPlot(mpg ~ wt, data = mtcars, color = "gear", type = "point")
n1$save('n1.html', cdn = TRUE)

```

<iframe width = 100% height = 60%  src='n1.html'></iframe>


```{r}
n1$addControls("x", value = "wt", values = names(mtcars))
n1$addControls("y", value = "wt", values = names(mtcars))
n1$addControls("color", value = "gear", values = names(mtcars))
n1$save('n2.html', cdn = TRUE)
```

<http://stackoverflow.com/questions/21820197/nplot-in-rcharts-does-not-work-with-addcontrols>

- The addControls method has not been implemented for all libraries. It only works for nvd3, polychart and dimple. 

<iframe width = 100% height = 60%  src='n2.html'></iframe>



## Interactive Controls and rCharts 2

### rCharts dimple with Angular Controls

참고 : <http://bl.ocks.org/timelyportfolio/6459298#code.R>

```{r}
data <- read.delim(
"http://pmsi-alignalytics.github.io/dimple/data/example_data.tsv"
)

#eliminate . to avoid confusion in javascript
colnames(data) <- gsub("[.]","",colnames(data))
d1 <- dPlot(
x ="Month" ,
y = "UnitSales",
data = data,
type = "area"
)

d1$xAxis(orderRule = "Date")
d1$addControls("y", value = "UnitSales", values = names(data))
d1$addControls("groups", value = "", values = names(data))
d1$save('d1.html', cdn = TRUE)
```

<iframe width = 100% height = 60%  src='d1.html'></iframe>



## Interactive Controls and rCharts 3

참고 : <http://www.r-bloggers.com/interactive-charts-with-rcharts/>

```{r}

```
