---
title: "linear vs nonlinear"
output: html_document
---
????????????: The R book

#????????? ?????? ?????? ??? ????????? ????????? ????????? ???????????? ?????? 
(????????? ??? ?????????)

##????????? ??????
??? linear regression (the simplest, and much the most frequently used);
??? polynomial regression (often used to test for non-linearity in a relationship);
??? piecewise regression (two or more adjacent straight lines);
??? robust regression (models that are less sensitive to outliers);
??? multiple regression (where there are numerous explanatory variables);
??? non-linear regression (to fit a specified non-linear model to data);
??? non-parametric regression (used when there is no obvious functional form).

??? ????????? ?????? ?????? ???

###?????? ?????? ??????
???: ????????? ????????? ???????????? ????????? ???????????? ???????????? ?????????????????? ?????? ???????????? ?????????!

????????? ?????? ?????? ?????? ????????? ??????????????? ?????? ????????? ???????????? ??? ???
????????? ?????? ??????(generalized linear)
????????? ?????? ????????? ??????????????? ???????????? ???????????? ?????? ???????????? ????????? ??? ??????.


?????? ?????? ????????? ?????? ??????
??? ?????? ?????? ????????? ???????????????
??? ?????? ????????? ?????? ?????? ????????? ????????????
(????????? ??????????????? ??? ?????? ????????? ??????????????? ?????? ??????????????? ?????? ????????? ??????.
??? ?????? ????????? ?????? ?????? ??????????????? ????????????.)
??? ?????? ????????? ?????? ??????(correlation)
??? ?????? ?????? ??? ?????? ??????
??? ?????? ????????? ?????? ??????


????????? ??????
??? ???????????? ?????? ??????
??? ?????? ????????? ??????, ??????, ??????????????? ????????? ?????? ????????? ??????????


```{r}
ozone.pollution<-read.table("/Users/song-yeongsug/Documents/r/therbook/ozone.data.txt", header=T)
attach(ozone.pollution)
names(ozone.pollution)
```

?????? ?????? ??????????????? pairs??? ????????? ?????? ????????? ?????? ????????? ?????? ??????. 

```{r}
pairs(ozone.pollution,panel=panel.smooth)
````
y?????? ????????? ?????? ?????? ????????? ??????????????? ?????? ?????? ??????????????? ?????? ???????????? ?????? ?????? ????????? ?????????
???????????????????????? ?????? ???????????? ????????? ??????. 

?????? ?????? ????????? ???????????? ?????? ????????? ?????? ??????(generalized additive model)?????? ????????? ????????? ??????

```{r}
library(mgcv)
par(mfrow=c(2,2))
model<-gam(ozone~s(rad)+s(temp)+s(wind))
plot(model)
par(mfrow=c(1,1))
```

?????? ????????? ????????? ???????????? ????????? ????????? ????????? ???????????? ?????? ????????? ????????? ??? ??? ?????? ?????? ????????? ??????. ????????? ???????????????????????? ???????????? ?????? ????????? ????????? ??? ??? ??????. ??? ???????????? ????????? ????????? ?????? ??????????????? ?????? ????????? ???????????? ??? ?????? ????????????. ??????????????? ????????? ?????? ???????????? ?????? ????????? ????????? ?????? ??????


```{r}
library(tree)
model<-tree(ozone~.,data=ozone.pollution)
plot(model)
text(model)
```

```{r}
w2 <- wind^2
t2 <- temp^2
r2 <- rad^2
tw<-temp*wind
wr<-wind*rad
tr<-temp*rad
wtr<-wind*temp*rad
```

```{r}
model1<-lm(ozone~rad+temp+wind+t2+w2+r2+wr+tr+tw+wtr)
summary(model1)
```


?????? ?????? ????????? ??????????????? ????????????. R??? ????????? ????????? p?????? ???????????? p????????? ????????? ???????????? ????????? ????????? ???????????? ?????? ???????????? ????????? ????????? ??????.


?????? ???????????? ?????? ????????????????????? ????????????????????? ????????????. 
????????????????????? ????????? ??????????????? ???????????? ???????????? ????????????. 
????????? ????????? ????????????(tw)??? ?????? ??????????????? ????????????.
????????? ???????????? ????????? ????????????(wr)??? ????????????. 
```{r}
model2<-update(model,~.-wrt)
summary(model2)
```


```{r}
model3<-update(model2,~.-r2)
summary(model3)

```


```{r}
model4<-update(model3,~.-tr)
summary(model4)
````


```{r}
model5<-update(model4,~.-tw)
summary(model5)
```



```{r}
model6<-update(model5,~.-wr)
summary(model6)
```


???????????? ?????? 6??? ????????????.
```{r}
par(mfrow=c(2,2))
plot(model6)
```

??? ????????? ?????? ??????. ????????? ???????????? ??????????????? ???????????? ??????(?????? vs  fitted)??? ??????????????? ?????? ??????????????? ????????? ?????????. ?????? ???????????? ?????? ?????? ????????? ????????? ?????? ????????????. ?????? ?????? ????????? ???????????? ????????? ????????? ????????? ?????? ?????? ????????? ?????? ???????????? ?????? ????????? ???????????????.
```{r}
model7<-lm(log(ozone)~rad+temp+wind+t2+w2+r2+wr+tr+tw+wtr)
summary(model7)
```


```{r}
model8<-update(model7,~.-wtr)
summary(model8)
model9<-update(model8,~.-tr)
summary(model9)
model10<-update(model9,~.-tw)
summary(model10)
model11<-update(model10,~.-t2)
summary(model11)
model12<-update(model11,~.-wr)
summary(model12)
```



```{r}
plot(model2)
```

?????? ????????? 5?????? ????????? ????????? ?????? ???????????? ????????? ??????. ?????? ?????? ????????? ????????? ?????? ????????? ?????? ?????? 0??? ??? ?????? ????????? ???????????? ??????????????? ????????? ??????. ?????? ???????????? ????????? ?????? ?????? ?????? ????????? ?????? ????????? ???????????? ?????? ????????????.
???????????? ????????? ?????? ????????? ?????????. ?????? ?????????????????? ??????????????? ?????? ??????(??????) ???????????? ?????? ????????? ????????? ?????? ?????? ????????? ??????????????? ????????? ????????? 70% ?????? ??????????????? ??? ??? ??????. 
????????? ????????? ???????????? ????????? ????????? ?????? ?????? ??? ????????? ???????????? ??? ???



