Ch4. Line graph
========================================================
변수 X에 대한 변수 Y의 값의 변화

### 4.1. Making a Basic Line Graph

Basic line graph :

```{r fig.width=5, fig.height=4}
library(ggplot2)
BOD
ggplot(BOD, aes(x=Time, y=demand)) + geom_line()

```

When x is a categorical variable by converting it to a factor with factor() :

```{r fig.width=5, fig.height=4}
BOD1 <- BOD # Make a copy of the data
BOD1$Time <- factor(BOD1$Time)

BOD1$Time
BOD$Time

ggplot(BOD1, aes(x=Time, y=demand, group=1)) + geom_line()
#When the x variable is a factor, you must also use aes(group=1) to ensure that ggplot() knows that the data points belong together and should be connected with a line :
```

```{r fig.width=5, fig.height=4}
ggplot(BOD, aes(x=Time, y=demand)) + geom_line() + ylim(0, max(BOD$demand))
# These have the same result
# ggplot(BOD, aes(x=Time, y=demand)) + geom_line() + expand_limits(y=0)
```
### 4.2. Adding Points to a Line Graph
```{r fig.width=5, fig.height=4}
ggplot(BOD, aes(x=Time, y=demand)) + geom_line() + geom_point()

library(gcookbook)

ggplot(worldpop, aes(x=Year, y=Population)) + geom_line() + geom_point()
ggplot(worldpop, aes(x=Year, y=Population)) + geom_line() + geom_point() +
scale_y_log10()
```

With the log y-axis, you can see that the rate of proportional change has increased in the last thousand years. We can also see that the population estimates are much more frequent in recent times—and probably more accurate!


### 4.3. Making a Line Graph with Multiple Lines
```{r fig.width=5, fig.height=4}
# Load plyr so we can use ddply() to create the example data set
# ddply : Split data frame, apply function, and return results in a data frame

library(plyr)
ToothGrowth
# Summarize the ToothGrowth data

tg <- ddply(ToothGrowth, c("supp", "dose"), summarise, length=mean(len))
tg
str(tg)
# Map supp to colour
ggplot(tg, aes(x=dose, y=length, colour=supp)) + geom_line()
# Map supp to linetype
ggplot(tg, aes(x=dose, y=length, linetype=supp)) + geom_line()
# the x-axis is conceived of as being categorical
ggplot(tg, aes(x=factor(dose), y=length, colour=supp, group=supp)) + geom_line()
# without group=supp, error happen.
ggplot(tg, aes(x=factor(dose), y=length, colour=supp)) + geom_line()
ggplot(tg, aes(x=dose, y=length)) + geom_line()
```

This happens because there are multiple data points at each y location, and ggplot() thinks they’re all in one group.

```{r fig.width=5, fig.height=4}
ggplot(tg, aes(x=dose, y=length, shape=supp)) + geom_line() +
geom_point(size=4) # Make the points a little larger
ggplot(tg, aes(x=dose, y=length, fill=supp)) + geom_line() +
geom_point(size=4, shape=21) # Also use a point with a color fill
ggplot(tg, aes(x=dose, y=length, shape=supp)) +
geom_line(position=position_dodge(0.2)) + # Dodge lines by 0.2
geom_point(position=position_dodge(0.2), size=4) # Dodge points by 0.2
```
### 4.4. Changing the Appearance of Lines
```{r fig.width=5, fig.height=4}
ggplot(tg, aes(x=dose, y=length, colour=supp)) +
geom_line() + scale_colour_brewer(palette="Set1")
ggplot(tg, aes(x=dose, y=length, colour=supp)) +
geom_line(linetype="dashed") +
geom_point(shape=22, size=3, fill="white")

```
### 4.5. Changing the Appearance of Points
```{r fig.width=5, fig.height=4}
ggplot(BOD, aes(x=Time, y=demand)) +
geom_line() +
geom_point(size=4, shape=22, colour="darkred", fill="pink")
# The default shape for points is a solid circle, the default size is 2, and the default colour is "black".

# Summarize the ToothGrowth data
tg <- ddply(ToothGrowth, c("supp", "dose"), summarise, length=mean(len))

# Save the position_dodge specification because we'll use it multiple times

pd <- position_dodge(0.2)

ggplot(tg, aes(x=dose, y=length, fill=supp)) +
geom_line(position=pd) +
geom_point(shape=21, size=3, position=pd) +
scale_fill_manual(values=c("black","white"))

```

### 4.6. Making a Graph with a Shaded Area

Use geom_area() to get a shaded area.
```{r fig.width=8, fig.height=4}
sunspot.year
sunspotyear <- data.frame(Year = as.numeric(time(sunspot.year)),
Sunspots = as.numeric(sunspot.year))
head(sunspotyear)
ggplot(sunspotyear, aes(x=Year, y=Sunspots)) + geom_area()

# we will also make it 80% transparent by setting alpha to 0.2

ggplot(sunspotyear, aes(x=Year, y=Sunspots)) +
geom_area(colour="black", fill="blue", alpha=.2)
# we can draw the area without an outline (by not specifying colour)

ggplot(sunspotyear, aes(x=Year, y=Sunspots)) +
geom_area(fill="blue", alpha=.2) + geom_line()
```

### 4.7. Making a Stacked Area Graph
```{r fig.width=8, fig.height=4}
# Age distribution of population in the United States, 1900-2002
uspopage
str(uspopage)
ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup)) + geom_area()

# The default order of legend items is the opposite of the stacking order
# and adds thin(size=.2) lines between each area

ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup)) +
geom_area(colour="black", size=.2, alpha=.4) +
scale_fill_brewer(palette="Blues", breaks=rev(levels(uspopage$AgeGroup)))

# To reverse the stacking order, we put order=desc(AgeGroup) inside of aes()

ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup, order=desc(AgeGroup))) + geom_area(colour="black", size=.2, alpha=.4) +
scale_fill_brewer(palette="Blues")

# the outline includes the left and right sides.To get rid of it, first draw
# the stacked areas without an outline (by leaving colour as the default NA value), and then add a geom_line() on top:

ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup, order=desc(AgeGroup))) + geom_area(colour=NA, alpha=.4) +
scale_fill_brewer(palette="Blues") +
geom_line(position="stack", size=.2)
```

### 4.8. Making a Proportional Stacked Area Graph

```{r fig.width=8, fig.height=4}

# We use ddply() to split it into separate data frames for each value of Year, then apply the transform() function to each piece and calculate the Percent for each piece

uspopage_prop <- ddply(uspopage, "Year", transform,
Percent = Thousands / sum(Thousands) * 100)

head(uspopage_prop)
ggplot(uspopage_prop, aes(x=Year, y=Percent, fill=AgeGroup)) +
geom_area(colour="black", size=.2, alpha=.4) +
scale_fill_brewer(palette="Blues", breaks=rev(levels(uspopage$AgeGroup)))

```

### 4.9. Adding a Confidence Region
```{r fig.width=8, fig.height=4}
head(climate)
clim <- subset(climate, Source == "Berkeley", select=c("Year", "Anomaly10y", "Unc10y"))

clim

# In the climate data set, Anomaly10y is a 10-year running average of the 
# deviation (in Celsius) from the average 1950~1980 temperature, and Unc10y is the 95% confidence interval.

# Ribbons, y range with continuous x values.

ggplot(clim, aes(x=Year, y=Anomaly10y)) +
geom_ribbon(aes(ymin=Anomaly10y-Unc10y, ymax=Anomaly10y+Unc10y),
alpha=0.2) + geom_line()

# With a dotted line for upper and lower bounds

ggplot(clim, aes(x=Year, y=Anomaly10y)) +
geom_line(aes(y=Anomaly10y-Unc10y), colour="grey50", linetype="dotted") +
geom_line(aes(y=Anomaly10y+Unc10y), colour="grey50", linetype="dotted") +
geom_line()
```